Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-04-13 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex

To determine how people define CDRSs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage on which each user was presented with an image of the real room plus an image of the map data generated by the robot onto which the drawing could be done. The webpage (link removed for blind review) is shown in the inset in Figure~\ref{fig:ug40}. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

>>>>

To determine how people define CDSRs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage on which each user was presented with an image of the real room plus an image of the map data generated by the robot onto which the drawing could be done. The webpage\footnote{http://home.csumb.edu/k/katherinelockwood/world/} is shown in the inset in Figure~\ref{fig:ug40}. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.
